\documentclass[12pt]{resume}

\title{Charles `Nick' Hirzel}
\author{Charles `Nick' Hirzel}
\date{March 2023}

% margins
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textwidth}{7.5in}
\setlength{\textheight}{11in}
\setlength{\topmargin}{-0.5in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\evensidemargin}{-0.5in}

\pagestyle{empty}
\raggedbottom{}
\raggedright{}
\setlength{\tabcolsep}{0in}

% doc time
\begin{document}

% contact
\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}l}
    \multirow{3}{*}{{\fontsize{34pt}{12pt}\selectfont Charles (Nick) Hirzel}}
    & \href{mailto:hirzel.nick@gmail.com}{hirzel.nick@gmail.com}\\
    & +1 (567) 376-0770\\
    & Wilmington, DE\\
\end{tabular*}

% experience
\vspace{-1.00em}
\section{Work Experience}
\vspace{-0.5em}
\rule{7.5in}{0.2pt}

\vspace{0.15em}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\underline{{\fontsize{14pt}{0pt}\selectfont{JPMorgan Chase}}}: Software Engineer II \textit{(Hybrid)} & \textit{June 2023 - July 2024}
\end{tabular*}
\vspace{-1.75em}
\begin{itemize}
    \item \textbf{Engineered modern, low-latency Java Spring Boot microservices} distributed on AWS, successfully replacing monolithic legacy systems while improving system availability.
    \item \textbf{Led test-driven development initiatives}, leveraging JUnit, Hoverfly, and Cucumber \textbf{raising automated testing coverage above  80\%}, significantly reducing staging issues and accelerating release cycles.
    \item \textbf{Designed and implemented Datadog dashboards to aggregate metrics for more than 30 microservices}, accelerating root cause analysis and providing greater visibility to support data-driven decisions.
    \item \textbf{Streamlined deployment pipelines} by introducing advanced CI/CD workflows utilizing Terraform and Kubernetes, \textbf{cutting deployment times from over 2 hours to less than 5 minutes} and enhancing operational quality.
    \item \textbf{Coordinated seamless production updates} across critical services by aligning cross-functional teams and orchestrating detailed staging plans \textbf{to achieve zero downtime releases.}
\end{itemize}

\vspace{0em}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\underline{{\fontsize{14pt}{0pt}\selectfont{Law Office of Gerard Lynch}}}: Software Engineer \textit{(Remote)} & \textit{May 2021 - June 2023}
\end{tabular*} 
\vspace{-1.75em}
\begin{itemize}
    \item \textbf{Managed the complete migration of a legal case database spanning more than 35 years}, developing a multithreaded Python ETL pipeline with Flask, Pandas, and Numpy.
    \item \textbf{Developed workflow automations} using Google Suite integrations to automatically fill standard client letters and forms, eliminating errors and \textbf{saving approximately 30 hours weekly in clerical work.}
\end{itemize}

\vspace{0em}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\underline{{\fontsize{14pt}{0pt}\selectfont{Wright State University}}}: Laboratory Instructor \& Tutor \textit{(Hybrid)} & \textit{May 2019 - May 2021}
\end{tabular*}
\vspace{-1.75em}
\begin{itemize}
    \item \textbf{Instructed over 50 students in computer science lab sections} and graded student projects weekly, demanding rapid code comprehension and objective evaluation.
    \item \textbf{Developed automated testing tools} for student projects, \textbf{halving the grading time per submission} and significantly improving grading accuracy.
    \item \textbf{Tutored at least 20 students weekly} in various CS topics including Java and Assembly programming, algorithm and data structure design, and theoretical computer science.
\end{itemize}

\vspace{0em}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\underline{{\fontsize{14pt}{0pt}\selectfont{Hirzel Canning Company}}}: Various Roles \textit{(On-Site)} & \textit{June 2010 - Feb. 2017}
\end{tabular*}
\vspace{-1.75em}
\begin{itemize}
    \item \textbf{Supported process-critical hardware and IT systems across 3 locations}, requiring deep knowledge of plant systems and operations.
    \item \textbf{Conducted 500+ laboratory-based quality tests} (e.g., pH, calcium titration) using standard analytical procedures; validated results, and escalated anomalies to process engineers.
\end{itemize}

\vspace{-1em}

% education
\section{Education}
\vspace{-0.5em}
\rule{7.5in}{0.2pt}
\vspace{-0.75em}\\

\begin{tabular*}{7.5in}{ l@{\extracolsep{1em}} l@{\extracolsep{\fill}} r }
{\fontsize{14pt}{0pt}\selectfont{Wright State University}} & \textbf{B.S. in Computer Science} & \textit{Aug. 2018 - May 2021}\\
\vspace{-1em}\\
{\fontsize{14pt}{0pt}\selectfont{Certifications}} & \textbf{AWS Cloud Practitioner} & \textit{Aug. 2023}\\
\vspace{-1em}\\
\end{tabular*}
{\fontsize{14pt}{0pt}\selectfont{Skills}}: Java, Python, C++, C, Bash, Git, Linux, SQL, AWS (EC2, ECS, EKS), Terraform, Kubernetes, CI/CD, DevOps, Pandas, Numpy, JUnit, Automated Testing, ETL Pipelines, Parallel Computing, HPC, Networking, Graphics Programming, Numerical Methods

\end{document}